Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
curves: in cong ex, re-cite thm 9.3.1
fixed jorge's name

If $\Gamma$ has no nonzero odd weight modular forms, then $\Gamma$ is generated in weight at most $6$ with relations in weight at most $12$. This follows from work by Voight and Zureick-Brown \cite[Theorem 1.4]{vzb:stacky}. Note that the exceptional cases of their result \cite[Theorem 9.3.1]{vzb:stacky}, which happen when the genus is zero, do not occur because $\delta > 0$.

@@

\section{Acknowledgments}
We are grateful to David Zureick-Brown for introducing us to the
study of stacky canonical rings, for providing invaluable guidance,
and for his mentorship. We also thank Ken Ono and the Emory
University Number Theory REU for arranging our project and
providing a great environment for mathematical learning and
collaboration. We thank Jorge Sentieiro Neves for pointing out the
bounds given by Miles Reid's work on the maximal degrees of minimal
generators and relations of spin canonical rings in high genera. We
also thank Brian Conrad and John Voight for helpful comments on
this paper. The first author would also like to mention Joseph
Harris and Evan O'Dorney for several enlightening conversations
related to Petri's Theorem. Finally, we gratefully acknowledge the
support of the National Science Foundation (grant number DMS-1250467).
We deeply appreciate all of the support that has made our work
possible.

>>>>

If $\Gamma$ has no nonzero odd weight modular forms, then $\Gamma$ is generated in weight at most $6$ with relations in weight at most $12$. This follows from work by Voight and Zureick-Brown \cite[Theorem 1.4 and Theorem 9.3.1]{vzb:stacky}. Note that the exceptional cases of their result \cite[Theorem 9.3.1]{vzb:stacky}, which happen when the genus is zero, do not occur because $\delta > 0$.

@@

\section{Acknowledgments}
We are grateful to David Zureick-Brown for introducing us to the
study of stacky canonical rings, for providing invaluable guidance,
and for his mentorship. We also thank Ken Ono and the Emory
University Number Theory REU for arranging our project and
providing a great environment for mathematical learning and
collaboration. We thank Jorge Neves for pointing out the
bounds given by Miles Reid's work on the maximal degrees of minimal
generators and relations of spin canonical rings in high genera. We
also thank Brian Conrad and John Voight for helpful comments on
this paper. The first author would also like to mention Joseph
Harris and Evan O'Dorney for several enlightening conversations
related to Petri's Theorem. Finally, we gratefully acknowledge the
support of the National Science Foundation (grant number DMS-1250467).
We deeply appreciate all of the support that has made our work
possible.
